\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-13 Articles/IROS/root.tex
added 2D keyframes
added 2 columns view
added ball figures

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{keyframes_3D.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-3d-column}
\end{figure}

@@

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_3D.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-3d-column}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_2D_a.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-2d-column}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_2_columns.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-2-column}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_3D_ball.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-3d-ball}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_2D_ball.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-2d-ball}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{keyframes_2_columns_ball.eps} % Replace 'example-image' with the filename of your image
	\caption{Example Image}
	\label{fig:keyframes-2-column-ball}
\end{figure}
